---
title: "RAiN analysis"
author: "Nicolas Legewie"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

##### Load packages #####

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, cowplot, excluder)


##### Set version ##### I think we don't need this bit here

# version <- 'pretest'
version <- 'fullsurvey'


##### Set wd #####

Paths <- c("/Users/neikos/Documents/work/Stat_code_R_RAiN networks/rain_networks/", 
          "YOUR PATH")

names(Paths) = c("neikos", "YOUR USERNAME")

setwd(Paths[Sys.info()[7]])

##### Load data #####

### Load main data ###
files <- file.info(list.files("data/", full.names = TRUE))
files_filtered <- filter(files, grepl("rds", row.names(files))) %>% filter(grepl("fullsurvey", row.names(.)))
clean_data <- readRDS(rownames(files_filtered)[order(rownames(files_filtered))][nrow(files_filtered)])

### Load Batch rejection data ###
mturk_batches <- read_csv('data/Batch_1_results.csv') %>% 
  mutate(batch = 1) %>% 
  bind_rows(mutate(read_csv('data/Batch_2_results.csv'), batch = 2)) %>% 
  bind_rows(mutate(read_csv('data/Batch_3_results.csv'), batch = 3)) %>% 
  filter(AssignmentStatus == "Rejected")

### Load rIP output ###
ip_files_filtered <- filter(files, grepl("rds", row.names(files))) %>% filter(grepl("IPaddress", row.names(.)))
IPcheck_output <- readRDS(rownames(ip_files_filtered)[order(rownames(ip_files_filtered))][nrow(ip_files_filtered)])

### Load raw Qualtrics data ###

IPcheck_data_raw <- read_csv(glue("data/qualtrics_{version}_raw_{lubridate::today()}.csv"))


### Remove Rejected Data ###

clean_data_noRejects <- clean_data %>% 
  anti_join(mturk_batches, by= c("MID" = "WorkerId"))

### Create data with complete alter data ###
clean_data_completeAlterdata <- clean_data %>% 
    drop_na(alter_data)

clean_data_noRejects_completeAlterdata <- clean_data_noRejects %>% 
    drop_na(alter_data)


##### Load fonts #####
loadfonts()


##### Define themes #####

main_theme <- theme_light() + 
              theme(
                text = element_text(size = 12, family = "Merriweather Sans"),
                plot.margin = unit(rep(1, 4), "cm"),
                axis.title.x = element_text(margin = margin(15, 0, 0, 0)),
                axis.title.y = element_text(margin = margin(0, 15, 0, 0)))


main_theme_noMargin <- theme_light() + 
              theme(
                text = element_text(size = 12, family = "Merriweather Sans"),
                axis.title.x = element_text(margin = margin(15, 0, 0, 0)),
                axis.title.y = element_text(margin = margin(0, 15, 0, 0)))


main_theme_noMargin_smallFont <- theme_light() + 
              theme(
                text = element_text(size = 10, family = "Merriweather Sans"),
                axis.title.x = element_text(margin = margin(15, 0, 0, 0)),
                axis.title.y = element_text(margin = margin(0, 15, 0, 0)))

```


### To Do

* Check Small stuff for angles  
  
* Add to data quality: by Batch, comparison excluded v. included
* Change SES of origin in demo & SES descriptives to highest degree between two parents   
* Change histograms to percent  
* Fix issue with code for `act_instancesEmo`: For two respondents output is `-Inf`  
* Income descr plot: NAs are not displayed  
* Rate of match: Activation ties v. "important ties"
* Differences in tie numbers: age, gender, race, education, income  
* Differences in activation instances: age, gender, race, SES  
* Differences in rate of match: age, gender, race, SES  
  
  
  
  
### Data quality
  
Overall, our analysis suggests that about 10% of our initial respondents were in fact not US residents.
  
  
```{r data_quality, echo = FALSE, message = FALSE, warning = FALSE}

# IPHub

rIP <- IPcheck_output %>% 
  summarize(
    source = "rIP",
    perc_nonUS = sum(IP_Hub_nonUSIP) / n(),
    perc_VPS = sum(IP_Hub_VPS) / n(),
    perc_blockRec = sum(IP_Hub_recommend_block) / n()) %>% 
  pivot_longer(
    contains("perc_"),
    names_to = "statistic",
    values_to = "value")

# excluder

excluder <- clean_data %>% 
  summarize(
    source = "excluder",
    perc_duplicateIP = IPcheck_data_raw %>% check_duplicates(dupl_location = FALSE) %>% nrow() / nrow(IPcheck_data_raw),
    perc_IPnonUS = IPcheck_data_raw %>% check_ip(country = "US") %>% nrow() / nrow(IPcheck_data_raw),
    perc_locNonUS = IPcheck_data_raw %>% check_location() %>% nrow() / nrow(IPcheck_data_raw)) %>% 
  pivot_longer(
    contains("perc_"),
    names_to = "statistic",
    values_to = "value")

# Bind

full_IPcheck <- rIP %>% 
  bind_rows(excluder)

# Visualize

full_IPcheck %>%
  ggplot(aes(statistic, value, fill = source)) +
  geom_col() +
  main_theme_noMargin_smallFont +
  facet_wrap(.~source) +
  coord_flip()


```
  
  
It seems like the people with suspicious IP addresses are not the one's we reject because of bad data. The values from the three checks provided by the excluder package remain virtually the same after removing our rejects. Maybe there's an error in my data generating code in the setup chunk?
  
  
```{r data_quality_noRejects, echo = FALSE, message = FALSE, warning = FALSE}

clean_data_noRejects %>% 
  summarize(
    perc_duplicateIP = IPcheck_data_raw %>% check_duplicates(dupl_location = FALSE) %>% nrow() / nrow(IPcheck_data_raw),
    perc_IPnonUS = IPcheck_data_raw %>% check_ip(country = "US") %>% nrow() / nrow(IPcheck_data_raw),
    perc_locNonUS = IPcheck_data_raw %>% check_location() %>% nrow() / nrow(IPcheck_data_raw)) %>% 
  pivot_longer(
    everything(),
    names_to = "statistic",
    values_to = "value") %>%
  ggplot(aes(statistic, value, fill = statistic)) +
    geom_col(show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip()


read_csv('data/Batch_1_results.csv') %>% 
    mutate(batch = 1) %>% 
    bind_rows(mutate(read_csv('data/Batch_2_results.csv'), batch = 2)) %>% 
    bind_rows(mutate(read_csv('data/Batch_3_results.csv'), batch = 3)) %>%

Fri Dec 03 18:50:18 PST 2021 Batch 1
Sat Dec 04 17:04:18 PST 2021 Batch 2



```
    
  
  
  
### Descriptive statistics

## Demographics and SES
  
  
The plots show that our sample scews young, male, white, highly educated, and above-average income (I think?). Almost all respondents said they were employed full time. In terms of parents' level of education, too, the sample scews highly educated. I wonder if we will be able to get enough obs in all cells in order to run post-stratification. Especially race seems to be problematic.
  
  
```{r descriptives_demoSES, echo = FALSE, message = FALSE, warning = FALSE}

# Age: desnity plot
age_descrPlot <- clean_data_noRejects %>%
  ggplot(aes(as.numeric(age))) +
    geom_density() +
    main_theme_noMargin_smallFont

# Gender: Bar plot
gender_descrPlot <- clean_data_noRejects %>%
  ggplot(aes(gender, fill = gender)) +
    geom_bar(aes(y = (..count..)/sum(..count..)), show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip()

# Race: Bar plot
race_descrPlot <- clean_data_noRejects %>%
  mutate(race = ifelse(hispanic == "Yes", "White Hispanic", race)) %>%
  ggplot(aes(race, fill = race)) +
    geom_bar(aes(y = (..count..)/sum(..count..)), show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip()

# Education: Bar plot
educ_descrPlot <- clean_data_noRejects %>%
  ggplot(aes(educ, fill = educ)) +
    geom_bar(aes(y = (..count..)/sum(..count..)), show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip()

# Income: Bar plot
income_descrPlot <- clean_data_noRejects %>%
  ggplot(aes(income, fill = income)) +
    geom_bar(aes(y = (..count..)/sum(..count..)), show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip()

# Employment status: Bar plot
employm_descrPlot <- clean_data_noRejects %>%
  ggplot(aes(employment, fill = employment)) +
    geom_bar(aes(y = (..count..)/sum(..count..)), show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip()

# Education: Bar plot

parentEduc_descrPlot <- clean_data_noRejects %>%
  select(father_ed, mother_ed) %>%
  pivot_longer(everything(),
               names_to = "parent",
               values_to = "education") %>%
  ggplot(aes(education, fill = parent)) +
    geom_bar(aes(y = (..count..)/sum(..count..)), show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    coord_flip() +
  facet_wrap(.~parent)


# Display plots
# plot_grid(
#   plotlist = list(age_descrPlot,
#                   gender_descrPlot,
#                   race_descrPlot,
#                   educ_descrPlot,
#                   income_descrPlot,
#                   employm_descrPlot),
#   ncol = 2)

age_descrPlot
gender_descrPlot
race_descrPlot
educ_descrPlot
income_descrPlot
employm_descrPlot
parentEduc_descrPlot


```
  
  
  
  
## Personal network and support activation
  
  
The plots show that we have what I believe to be a data quality problem: Many people seem to fill out all windows when asked for activation examples, alters they talked to in each example, and important people. Not sure how we can fix this. With activation alters, we may exclude, as a robustness check at least, everyone who filled out all 9 possible activation examples, and all alters for each example. With important people we probably shouldn't do anything, it's very possible that many people fill out all five slots for both family and non-family important people. Maybe we could exclude those people here as well who filled up everything for tie activation.
  
  
  
```{r descriptives_networks, echo = FALSE, message = FALSE, warning = FALSE}

# Define helper function

# clean_data$important_people[[1]] %>% select(important_alter_name) %>% bind_rows(clean_data$alter_data[[1]] %>% select(alter_name)) %>% mutate(alter_name = ifelse(is.na(alter_name), important_alter_name, alter_name)) %>% select(alter_name) %>% distinct() %>% nrow()

# try n_distinct

get_nTiesTotal.fun <- function(x, y) {
x %>% select(important_alter_name) %>% bind_rows(y %>% select(alter_name)) %>% mutate(alter_name = ifelse(is.na(alter_name), important_alter_name, alter_name)) %>% select(alter_name) %>% distinct() %>% nrow()
}


### Number of ties
# Generate data

# mutate(nTiesAct = clean_data %>% drop_na(alter_data) %>% .[,44] %>% pull() %>% map_dbl(nrow(distinct(., alter_name))))

nTiesAct_descriptives <- clean_data_noRejects_completeAlterdata %>%
    mutate(nTiesAct = map_dbl(.[,44] %>% pull(), ~nrow(distinct(., alter_name)))) %>% 
    select(ResponseId, MID, nTiesAct)
         
nTiesImp_descriptives <- clean_data_noRejects %>% 
    drop_na(important_people) %>%
    mutate(nTiesImpFamily = map(.[,43] %>% pull(), ~.x %>% count(important_alter_type) %>% .[1,2]) %>% map_dfr(as_tibble, .name_repair = "universal") %>% pull(),
           nTiesImpNonFamily = map(.[,43] %>% pull(), ~.x %>% count(important_alter_type) %>% .[2,2]) %>% map_dfr(as_tibble, .name_repair = "universal") %>% pull()) %>%
    select(ResponseId, MID, nTiesImpFamily, nTiesImpNonFamily)


nTiesTotal_descriptives <- clean_data_noRejects_completeAlterdata %>%
    drop_na(important_people) %>%
    mutate(nTiesTotal = map2_dbl(.[,43] %>% pull(), .[,44] %>% pull(), get_nTiesTotal.fun)) %>%
    select(ResponseId, MID, nTiesTotal)


nTies_descriptives <- clean_data_noRejects %>%
  select(ResponseId, MID) %>%
  left_join(nTiesAct_descriptives) %>%
  left_join(nTiesImp_descriptives) %>%
  left_join(nTiesTotal_descriptives) %>%
  pivot_longer(cols = starts_with("nTies"),
               names_to = "tie_type",
               values_to = "n")


# Create plot
nTies_descriptives %>%
  ggplot(aes(n, fill = tie_type)) +
    geom_histogram(show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    facet_wrap(.~tie_type, scales = "free")



### Activation instances
# Generate data
nActivation_descriptives <- clean_data_noRejects_completeAlterdata %>%
  mutate(act_instancesTotal = map_dbl(.[,44] %>% pull(), ~nrow(distinct(., activation_instance_example))),
         act_instancesEmo = map(.[,44] %>% pull(), filter, activation_type == "emo") %>% map(select, activation_instance) %>% map_dbl(max),
         act_instancesInfo = map(.[,44] %>% pull(), filter, activation_type == "Info") %>% map(select, activation_instance) %>% map_dbl(max),
         act_instancesInst = map(.[,44] %>% pull(), filter, activation_type == "Inst") %>% map(select, activation_instance) %>% map_dbl(max)) %>% 
  select(act_instancesTotal, act_instancesEmo, act_instancesInfo, act_instancesInst) %>%
  pivot_longer(
    everything(),
    names_to = "activation_instance",
    values_to = "n"
  )


# Create plot
nActivation_descriptives %>%
  ggplot(aes(n, fill = activation_instance)) +
    geom_histogram(show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    facet_wrap(.~activation_instance, scales = "free")

```
  
  
  
Here's the plots with all respondents nTiesAct == 27 filtered out. Looking at the distributions of `nTiesAct` and `nTiesTotal`, to me this looks more realistic. Still, it's probably better to use a filter based on more than one of our flags. For instance, the IP address check, as well as others.  
  
  
  
```{r descriptives_networks_filtered, echo = FALSE, message = FALSE, warning = FALSE}

### Number of Ties

clean_data_noRejects %>%
  select(ResponseId, MID) %>%
  left_join(nTiesAct_descriptives) %>%
  left_join(nTiesImp_descriptives) %>%
  left_join(nTiesTotal_descriptives) %>%
  filter(nTiesAct < 27) %>%
  pivot_longer(cols = starts_with("nTies"),
               names_to = "tie_type",
               values_to = "n") %>%
  ggplot(aes(n, fill = tie_type)) +
    geom_histogram(show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    facet_wrap(.~tie_type, scales = "free")


### Number of activation instances

clean_data_noRejects_completeAlterdata %>%
  left_join(nTiesAct_descriptives) %>%
  filter(nTiesAct < 27) %>%
  mutate(act_instancesTotal = map_dbl(.[,44] %>% pull(), ~nrow(distinct(., activation_instance_example))),
         act_instancesEmo = map(.[,44] %>% pull(), filter, activation_type == "emo") %>% map(select, activation_instance) %>% map_dbl(max),
         act_instancesInfo = map(.[,44] %>% pull(), filter, activation_type == "Info") %>% map(select, activation_instance) %>% map_dbl(max),
         act_instancesInst = map(.[,44] %>% pull(), filter, activation_type == "Inst") %>% map(select, activation_instance) %>% map_dbl(max)) %>% 
  select(act_instancesTotal, act_instancesEmo, act_instancesInfo, act_instancesInst) %>%
  pivot_longer(
    everything(),
    names_to = "activation_instance",
    values_to = "n") %>%
  ggplot(aes(n, fill = activation_instance)) +
    geom_histogram(show.legend = FALSE) +
    main_theme_noMargin_smallFont +
    facet_wrap(.~activation_instance, scales = "free")


```



```{r match_actTies_impTies, echo = FALSE, message = FALSE, warning = FALSE}

### Code snippets
# clean_data$alter_data[[1]] %>% filter(alter_name %in% (clean_data$important_people[[1]] %>% pull(important_alter_name)))

# clean_data$alter_data[[1]] %>% distinct(alter_name, .keep_all = TRUE) %>% count(important_alter_type) %>% filter(important_alter_type == "family") %>% pull(n)

# test <- clean_data_completeAlterdata %>%
#   mutate(data = map(alter_data, 
#     ~mutate(.x,
#             important_alter_type = as_factor(important_alter_type))
#   ))

# test$nTiesAct_impFam[purrr::is_empty(test$nTiesAct_impFam)] <- NA
# test$nTiesAct_impFam <- unlist(test$nTiesAct_impFam)

# clean_data_completeAlterdata %>%
#     mutate(nTiesAct = map_dbl(.[,44] %>% pull(), ~nrow(distinct(., alter_name))),
#            nTiesAct_impFam = as_vector(map(.[,44] %>% pull(), get_nImpTie.fun, "family")),
#            nTiesAct_impNonFam = as_vector(map(.[,44] %>% pull(), get_nImpTie.fun, "person"))) %>%
#     select(ResponseId, MID, nTiesAct, nTiesAct_impFam, nTiesAct_impNonFam)


### Define helper function

get_nImpTie.fun <- function(data, tie) {
data %>% distinct(alter_name, .keep_all = TRUE) %>% count(important_alter_type, .drop = FALSE) %>% filter(important_alter_type == tie) %>% pull(n)
}


### Create variables

clean_data_noRejects_completeAlterdata %>% 
    mutate(nTiesAct = map_dbl(.[,44] %>% pull(), ~nrow(distinct(., alter_name))),
           nTiesAct_impFam = map(.[,44] %>% pull(), get_nImpTie.fun, "family"),
           nTiesAct_impNonFam = map(.[,44] %>% pull(), get_nImpTie.fun, "person")) %>%
    select(ResponseId, MID, nTiesAct, nTiesAct_impFam, nTiesAct_impNonFam)









```

